Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-09 paper.tex

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}                     
\usepackage{pdfpages} 
\usepackage{rotating}

@@

    \begin{abstract} Text of abstract.  
    \end{abstract} 
    \tableofcontents
    \chapter{Introduction}
        In recent years, the volume of neuroimaging data acquired has exceeded
        both the storage and computation capacity of a standard research 
        lab workstation. With the advancement of data sharing technologies, 
        this data has been made widely available, however, accessibility to 
        such data remains limited due to infrastructural demands and lack of 
        performant software. Even with powerful infrastructure, such as High
        Performance Computing (HPC) infrastructure, software configured to 
        efficiently use resources is required to make execution time manageable
        . Ensuring efficient processing of data is 
        complex and limits accessibility to researchers with little programming 
        knowledge. Existing neuroimaging workflow engines primarily rely on HPC
        resource managers for performance and are therefore not well suited for
        BigData processing. As a result, frameworks for the efficient 
        processing of Big neuroimaging Data need to be developed.

@@

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM) being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            MATLAB engine frameworks, such as PSOM, SPM and AA; LONI; Taverna; 
            MapReduce; and Spark \tristan{you don't have to mention that Matlab has a JVM}. Nipype, FastR, Pydpiper are all Python-based platform 
            independent workflow engines and Toil and Galaxy are CWL-based 
            platform independent engines. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE and Nextflow are 
            not platform-independent, but can execute on macOS and Linux.

@@

    \clearpage
    \begin{sidewaysfigure}[!p]
        \caption{Summary table comparing the 17 workflow engines on four axes:
        workflow composition, performance, portability and reproducibility.}
        \includepdf[landscape=true]{Figures/summary.pdf}
    \end{sidewaysfigure} 
    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}

>>>>

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}                     
\usepackage{graphicx} 
\usepackage{rotating}

@@

    \begin{abstract}

    \end{abstract} 
    \tableofcontents
    \chapter{Introduction}
        In recent years, the volume of neuroimaging data acquired has exceeded
        both the storage and computation capacity of a standard research 
        lab workstation. With the advancement of data sharing technologies, 
        this data has been made widely available, however, accessibility to 
        such data remains limited due to infrastructural demands and lack of 
        performant software. Even with powerful infrastructure, such as High
        Performance Computing (HPC) infrastructure, software configured to 
        efficiently use resources is required to make execution time manageable
        . Ensuring efficient processing of data is 
        complex and limits accessibility to researchers with little programming 
        knowledge. Existing neuroimaging workflow engines primarily rely on HPC
        resource managers for performance and are therefore not well suited for
        BigData processing. As a result, frameworks for the efficient 
        processing of Big neuroimaging Data need to be developed.

@@

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM), running on the MATLAB
            engine, being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            LONI, Taverna, MapReduce and Spark. MATLAB engine frameworks include PSOM, SPM and AA. 
            Nipype, FastR, Pydpiper are all Python-based platform 
            independent workflow engines and Toil and Galaxy are CWL-based 
            platform independent engines. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE and Nextflow are 
            not platform-independent, but can execute on macOS and Linux.

@@

    \begin{sidewaysfigure}[!p]
        \centering
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Figures/summary.pdf}
        \caption{Summary table comparing the 17 workflow engines on four axes:
        workflow composition, performance, portability and reproducibility.}
    \end{sidewaysfigure} 
    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}
